### 2021-03-11 input/background.tex
removing inter AS, reorganizing for the sake of scoped broadcast

Fog infrastructures are distributed systems comprising heterogeneous
machines interconnected by communication links. We do not consider
byzantine processes.

\begin{definition}[Fog infrastructure]
  A fog infrastructure is a \underline{g}raph $G(V, E)$ of
  \underline{v}ertices $V$ and bidirectional \underline{e}dges $E \in
  V \times V$. Edges have symmetric \underline{w}eights $w_{ij} =
  w_{ji}$ with $i, j \in V$.
\end{definition}

\begin{definition}[Logical partition]
  A logical \underline{p}artition $P_s$ originated at a
  \underline{s}ource process $s \in V$ is a set of interconnected
  processes that do not belong to another logical partition. The set
  of sources is $S \subseteq V$.
\end{definition}

Processes belong to logical partitions depending on path weights. When
weights are about latency or hop numbers, the optimal partitioning
consists in processing the multiple destinations shortest path at each
process \REF.

\begin{definition}[Shortest path]
  A \underline{p}ath $\pi_{ij}$ from Process $i$ to Process $j$ is a
  sequence of vertices $[i, k_1, k_2, \ldots k_n, j]$ with $\forall
  0\leq m \leq n, \langle \pi_{ij}[m], \pi_{ij}[m+1] \rangle \in
  E$. Shortest \underline{p}aths $\Pi_{ij}$ are sets of paths such
  that there exists no lower sum of weights $|\Pi_{ij}|$ from $i$ to
  $j$.
\end{definition}

\begin{definition}[Optimal partitioning]
  The optimal partitioning $\mathcal{P}$ is a set of logical
  partitions such that each process belongs to a logical partition
  comprising its closest source process.  $\forall p \in P_{s_1\in S},
  \nexists P_{s_2 \in S}$ such that $|\Pi_{s_1p}| > |\Pi_{s_2p}|$.
\end{definition}

Processes use reliable asynchronous message passing to reach optimal
partitioning together. Process $s$ generates a message
$\alpha_s^0$. Upon \underline{r}eceipt $r_i(\alpha_s^{w})$, Process
$i$ knows that Process $s$ created a partition at a path length of
$w$. Process $i$ may choose to \underline{d}eliver $d_i(\alpha_s^{w})$
if it improves its partitioning. Process $i$ may choose to propagate
its change through \underline{b}roadcast $b_i(\alpha_s^w)$.  Without
global knowledge, processes only rely on their own behavior to deduce
the behavior of their neighbor processes.

\input{input/figdel.tex} %% figure positioning

\begin{definition}[\label{def:transitivedelivery}Transitive delivery]
  Transitive delivery ensures the system eventually converges to
  optimal partitioning:
  \begin{inparaenum}[(i)]
  \item (\textbf{termination}) processes do not need to propagate
    operations they do not deliver: $\forall \langle i, j \rangle \in
    E, \neg d_i(\alpha_{s}^w)\implies \neg
    d_j(\alpha_{s}^{w+w_{ij}})$;
  \item (\textbf{propagation}) operations delivered by a process may
    also benefit neighbor processes: $\forall \langle i, j \rangle \in
    E, d_i(\alpha_{s}^{w_1}) \implies
    d_j(\alpha_{s}^{w_1+w_{ij}}) \vee
    d_j(\alpha_{*}^{w_2 < w_1 + w_{ij}})$.
  \end{inparaenum}
\end{definition}

\begin{algorithm}
  \input{input/algoadd.tex}
  \caption{\label{algo:add}Adding a partition by Process $p$.}
\end{algorithm}

Algorithm~\ref{algo:add} shows the instructions that implement the
rules of Definition~\ref{def:transitivedelivery} to converge towards
optimal partitioning. Figure~\ref{fig:add} illustrates its behavior on
a system comprising 4 processes $a$, $b$, $c$, and $d$. Two processes
$a$ and $c$ concurrently create a partition. They initialize their own
state with the lowest possible bound $0$ (see
Line~\ref{line:lowestbound}), and send a message to each of their
neighbors by accumulating the corresponding edge weight (see
Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, Process $b$
receives $\alpha_{c}^{1}$. Since it improves its own partition
distance, it keeps it and forwards it to its neighbors. Process $b$
discards $\alpha_{b}^{1.5}$, for it does not improve its partition
distance. Processes $c$ and $d$ will never hear of Process $a$'s
partition. At scale, such \emph{scoped flooding} saves bandwidth by
limiting generated traffic to subsets of
processes~\cite{wang2015prodiluvian}. In Figure~\ref{fig:addD},
processes discard last transiting messages. The system converged to
the optimal partitioning.  Transitive relationships ensure that each
process gets its closest source while accumulation of weights ensures
that messages propagation terminates.  Interestingly, while the
receipt order of messages does not impact on local control information
($r_b(\alpha_a^{1.5}) \cdot r_b(\alpha_a^{1}) \Leftrightarrow
r_b(\alpha_a^{1}) \cdot r_b(\alpha_a^{1.5}) \implies
\TODO{d_b(\alpha_a^{1})}$), it impacts on control information
broadcast in the network ($r_b(\alpha_a^{1.5}) \cdot r_b(\alpha_a^{1})
\implies b_b(\alpha_{b}^{1.5}) \cdot b_b(\alpha_{b}^{1})$ while
$r_b(\alpha_a^{1}) \cdot r_b(\alpha_a^{1.5}) \implies
b_b(\alpha_a^{1})$).

While only adding logical partitions to the distributed system is
straightforward, removing them introduces additional complexity.

\begin{definition}[Dynamic optimal partitioning]
  A dynamic optimal partitioning is an optimal partitioning where the
  set of sources $S$ does not monotonically increase. We suffix this
  set with \underline{t}ime $t$ : $S(t)$.  Process $i$ joins the set
  of sources by \underline{a}dding its partition with messages
  $\alpha_i^{0}$: $Add(i \not\in S(t)) \implies i \in S(t+1)$; and
  leaves the set of sources by \underline{d}eleting its partition with
  messages $\delta_i$: $Del(i \in S(t)) \implies i \not\in S(t+1)$.
\end{definition}

Unfortunately, due to differences in receipt order of messages between
processes, stale information may stop prematurely the propagation of
relevant messages leading to inconsistent partitioning.
\TODO{Figure~\ref{fig:del} shows that.}

@@

\begin{problem}[\label{prob:intra}Consistent partitioning]
  How to enable \emph{consistent} dynamic optimal partitioning in
  dynamic network using scoped flooding?
\end{problem}

@@

\begin{figure}
  \begin{center}
    \input{input/figASmotivation.tex}
    \caption{\label{fig:ASmotivation}Scoped flooding extended to
      objects, processes do not know about all partitions that exist
      in the whole distributed system.}
  \end{center}
\end{figure}

To further improve scoped flooding in autonomous systems, processes
may belong to multiple partitions representing the objects they are
aware of. Figure~\ref{fig:ASmotivation} highlights the geo-distributed
nature of autonomous systems. Autonomous systems have topological
properties~\cite{nur2018geography} that processes can leverage to
avoid flooding the whole systems with control information about all
partitions. In Figure~\ref{fig:ASmotivation}, Process $e$ creates a
partition about a specific object, flooding Paris's AS to notify
neighboring processes of the object. However, it does not flood the
whole network, for control information stops at Process $b$. It
significantly saves bandwidth compared to broadcast since processes
below entrypoints of autonomous systems are order of magnitude more
numerous. Yet, Processes $c$ and $d$ know whom to ask when they need
to return an object they are unaware of. Processes remain efficient in
answering requests. \TODO{which is important for end users \REF.}

\begin{definition}[Partitions in asynchronous systems]
  Processes may hold multiple partitions \TODO{Use $\mathcal{P}$}
  \TODO{TODO} \TODO{or multi-partitioning?}
\end{definition}

\begin{problem}[\label{prob:inter}Inter-AS consistent partitioning]
  How to enable scoped flooding of objects in autonomous systems?
\end{problem}

Next Section presents our approach that solves these scientific
problems by relying on logical control information only.

>>>>

\TODO{More related work. More motivations etc. Maybe describe IPFS?}

%% \begin{definition}[Dynamic optimal partitioning]
%%   A dynamic optimal partitioning is an optimal partitioning where the
%%   set of sources $S$ does not monotonically increase. We suffix this
%%   set with \underline{t}ime $t$ : $S(t)$.  Process $i$ joins the set
%%   of sources by \underline{a}dding its partition with messages
%%   $\alpha_i^{0}$: $Add(i \not\in S(t)) \implies i \in S(t+1)$; and
%%   leaves the set of sources by \underline{d}eleting its partition with
%%   messages $\delta_i$: $Del(i \in S(t)) \implies i \not\in S(t+1)$.
%% \end{definition}

%% Unfortunately, due to differences in receipt order of messages between
%% processes, stale information may stop prematurely the propagation of
%% relevant messages leading to inconsistent partitioning.
%% \TODO{Figure~\ref{fig:del} shows that.}

@@

%% \begin{problem}[\label{prob:intra}Consistent partitioning]
%%   How to enable \emph{consistent} dynamic optimal partitioning in
%%   dynamic network using scoped flooding?
%% \end{problem}

@@

%% \begin{figure}
%%   \begin{center}
%%     \input{input/figASmotivation.tex}
%%     \caption{\label{fig:ASmotivation}Scoped flooding extended to
%%       objects, processes do not know about all partitions that exist
%%       in the whole distributed system.}
%%   \end{center}
%% \end{figure}

%% To further improve scoped flooding in autonomous systems, processes
%% may belong to multiple partitions representing the objects they are
%% aware of. Figure~\ref{fig:ASmotivation} highlights the geo-distributed
%% nature of autonomous systems. Autonomous systems have topological
%% properties~\cite{nur2018geography} that processes can leverage to
%% avoid flooding the whole systems with control information about all
%% partitions. In Figure~\ref{fig:ASmotivation}, Process $e$ creates a
%% partition about a specific object, flooding Paris's AS to notify
%% neighboring processes of the object. However, it does not flood the
%% whole network, for control information stops at Process $b$. It
%% significantly saves bandwidth compared to broadcast since processes
%% below entrypoints of autonomous systems are order of magnitude more
%% numerous. Yet, Processes $c$ and $d$ know whom to ask when they need
%% to return an object they are unaware of. Processes remain efficient in
%% answering requests. \TODO{which is important for end users \REF.}

%% \begin{definition}[Partitions in asynchronous systems]
%%   Processes may hold multiple partitions \TODO{Use $\mathcal{P}$}
%%   \TODO{TODO} \TODO{or multi-partitioning?}
%% \end{definition}

%% \begin{problem}[\label{prob:inter}Inter-AS consistent partitioning]
%%   How to enable scoped flooding of objects in autonomous systems?
%% \end{problem}

%% Next Section presents our approach that solves these scientific
%% problems by relying on logical control information only.

### 2021-03-11 input/conclusion.tex
meow
coloring figures, adding biblio, sketching abstract
removing inter AS, reorganizing for the sake of scoped broadcast

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../paper"
%%% End:

>>>>

As future work, we plan on enhancing the
\underline{I}nter\underline{P}lanetary \underline{F}ile
\underline{S}ystem (IPFS)~\cite{henningsen2020mapping} with dynamic
logical partitioning capabilities in order to improve its caching
policy of popular contents at marginal cost.

\noindent We also plan on further improving scoped broadcast between
multiple autonomous systems. Indeed, processes could leverage the
hierarchical properties of such topology~\cite{nur2018geography} to
avoid flooding the whole systems with control information about all
partitions.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../paper"
%%% ispell-local-dictionary: "english"
%%% End:

### 2021-03-11 input/proposal.tex
removing inter AS, reorganizing for the sake of scoped broadcast

\section{\NAME for Dynamic Partitioning}
\label{sec:proposal}

In this section, we introduce \NAME (\TODO{stands for}) and its
\underline{ex}tension \NAMEB, reactive protocols for logical
partitioning in autonomous systems the cost of which actually depends
on their usage: when the system becomes quiescent, processes
eventually converge to their respective partition and do not require
further communication afterward.

Each process is stateless, works autonomously and asynchronously, in a
peer-to-peer fashion. Each process broadcasts each change to its
neighborhood, for the state of its neighbors may depend on this change
as well. Yet, generated traffic remains \TODO{low} using scoped
flooding. Messages that carry changes travel through the network
depending on partition of processes, stopping as soon as they
encounter uninterested processes. We demonstrate that \NAME guarantees
consistent partitioning despite different order in message deliveries
from one process to another. While \NAME is a general purpose logical
partitioning protocol for dynamic networks, \NAMEB further reduces
generated traffic in the context of inter-autonomous systems by
leveraging the hierarchical properties of such networks.

This section starts by describing \NAME's functioning by detailing its
operation to avoid inconsistent states due to ordering and staleness
of delivered messages. Then, it describes its extension \NAMEB that
builds multiple broadcast layers ordered using local knowledge only.
Finally, it ends with a complexity analysis of proposed protocols.

\subsection{Intra-autonomous system partitioning}

@@

In this section, we aim at solving Problem Statement~\ref{prob:intra}
by proposing \NAME, a reactive logical partitioning protocol for
dynamic partitioning in dynamic networks.

\paragraph{Dynamic partitions.}
At any time, a process can become a source, hence adding a new
partition to the system. This partition eventually includes all
processes that are closer from this new source than any other else. We
described such protocol in Section~\ref{sec:background}. Processes
naturally converge towards their respective best partition by only
piggybacking a monotonically increasing distance in forwarded
messages. % \TODO{Traffic of each partition is contained to the
%  partition.}

@@

\subsection{Inter-autonomous system partitioning}

\begin{figure}
  \centering\input{input/figAS.tex}
  \caption{\label{fig:AS}Inter autonomous systems
    partitioning. \TODO{More about relative ordering of links at each
      process}}
\end{figure}

In this section, we aim at solving Problem Statement~\ref{prob:inter}
by proposing \NAMEB, an extension of \NAME, that enables dynamic
logical partitioning in inter-autonomous systems. It leverages
hierarchical properties of these networks to further improve on scoped
flooding.

Autonomous systems are geo-distributed networks. Heterogeneous
communication links. Hierarchy of communication links. Per-object
broadcast.

We leave the link handling to membership protocols~\REF. The ordering
of links can be done based on latency. For instance, from 0 to 100 ms,
rank 0, from 100 to 1s, rank 2 \ldots

\begin{algorithm}
  \input{input/algoaaaa.tex}
  \caption{\label{algo:aaaa}\NAMEB running at Process $p$ for dynamic
    partitioning in inter-autonomous systems.}
\end{algorithm}

Figure~\ref{fig:AS} shows an example of inter-AS logical partitioning
where each process ranks its communication links, and each process
forwards messages to its neighbors starting from the rank of the link
that triggered the receipt, to its highest rank neighbors. In this
example, Process $e$ adds a partition. It forwards the generated
message to all its neighbors as if it received it from its lowest rank
links. When Process $a$ receives $\alpha_e^1$ from its rank-$0$ link,
it forwards it to rank-$0$ links and rank-$1$ links.  Process $b$
stops the propagation, for all its links have lower ranks than the one
from which it received the message $\alpha_e^2$. Ultimately, the
partition includes Process $e$, Process $a$, and Process $b$. Process
$c$ and Process $d$ remain unaware of the new \TODO{object}.

To ease the reasoning about inter-AS dynamic partitioning in dynamic
networks, \NAME runs an independent broadcast protocol for each
object, and for each rank of links.  \TODO{Not so easy\ldots}
\TODO{Write and describe algo.} \TODO{Overhead of separating things,
  slightly more memory, but traffic wise? slower ?}  \TODO{In the
  example, not only Process $b$ keeps $e_1$ as its best partition, but
  it keeps it for links of rank 0, and links of rank 1.}  When there
are no ranking in links, processes solely rely on
Algorithm~\ref{algo:adddelundo} for optimal partitioning.

\subsection{Complexity}
\label{subsec:complexity}

>>>>

\section{Scoped broadcast}
\label{sec:scoped}

Fog infrastructures are distributed systems comprising heterogeneous
machines interconnected by communication links. We do not consider
byzantine processes.

\begin{definition}[Fog infrastructure]
  A fog infrastructure is a connected \underline{g}raph $G(V, E)$ of
  \underline{v}ertices $V$ and bidirectional \underline{e}dges $E
  \subseteq V \times V$.  A \underline{p}ath $\pi_{ij}$ from Process
  $i$ to Process $j$ is a sequence of vertices $[i, k_1, k_2, \ldots
    k_n, j]$ with $\forall m: 0\leq m \leq n, \langle \pi_{ij}[m],
  \pi_{ij}[m+1] \rangle \in E$.
\end{definition}

Processes can send messages to their neighboring processes. Processes
can reliably broadcast messages by forwarding delivered
messages~\cite{hadzilacos1994modular,nedelec2018causal,raynal2013distributed}. However,
uniform reliable broadcast states that \emph{all} correct processes
must deliver broadcast messages. This proves costly in large scale
systems comprising thousands of processes. Instead, we define
\emph{scoped broadcast} where messages reach only interested
processes, significantly reducing generated traffic.

\begin{definition}[\underline{S}coped broadcast (S-broadcast)]
  When Process $x$ scoped \underline{b}roadcasts $b_x(m)$ a
  \underline{m}essage $m$, every correct Process $y$ within a scope
  \underline{r}eceives $r_y(m)$ and \underline{d}elivers it
  $d_y(m)$. The scope depends on \underline{s}tates $\sigma$ of
  processes, \underline{m}etadata $\mu$ within received messages, and
  a \underline{p}redicate $\phi$ verified from process to process:
  $b_x(m) \wedge r_y(m) \implies \exists \pi_{xy} : \forall z \in
  \pi_{xy}, \phi(\mu_z, \sigma_z)$.
\end{definition}

This definition highlights the transitive relevance of messages and
encompasses more specific definitions of related
work~\cite{hsiao2005scoped,lue2006scoped,wang2015prodiluvian}.  A
process from Paris could scoped broadcast a message to all processes
in this city. A process from Paris could scoped broadcast a message to
all processes in this city plus neighboring cities by overloading
forwarded messages the first time they reach another city. Similarly
to reliable broadcast, scoped broadcast implementations expose
different trade-offs on space, time, and communication.

%% \begin{definition}[S-broadcast properties]
%%   S-broadcast guarantees 3 properties:
%%   \begin{inparaenum}[(i)]
%%   \item Validity: If a correct process broadcasts a message, it
%%     eventually delivers it;
%%   \item Scoped Agreement: If a process broadcasts a message, then all
%%     correct processes within the scope eventually delivers it;
%%   \item Scoped Integrity: A process delivers a message only if it was
%%     previously broadcast within the scope.
%%   \end{inparaenum}
%% \end{definition}

In this paper, we propose to dynamically adapt the scope of
S-broadcast using S-broadcast itself.  At any time, a process can
become the source of a new logical partition by transitively modifying
the respective state of neighboring processes using path weights.
When a process S-broadcasts a message in this partition, it reaches
all processes belonging to this partition. While the first partition
gathers all processes of the system, the following partitions reduce
the membership size of their neighboring partitions. In turns, the
traffic generated to adapt scopes scales with the number of
partitions.

\begin{definition}[Consistent partitioning]
  Let $S \subseteq V$ be the set of \underline{s}ources, $W_{xy} =
  W_{yx}$ be the symetric \underline{w}eight between $x$ and $y$,
  $\Pi_{xz}$ be the shortest \underline{p}ath from $x$ to $z$ the
  weight of which $|\Pi_{xz}|$ is lower than any other path weight,
  the consistent partitioning $\mathcal{P}$ is a set of logical
  partitions $P_{s\in S}$ such that each process belongs to a logical
  partition comprising its closest source process.  $\forall p \in
  P_{s_1}, \nexists P_{s_2}$ such that $|\Pi_{s_1p}| > |\Pi_{s_2p}|$.
\end{definition}

\input{input/figdel.tex} %% figure positioning

%% \begin{definition}[\label{def:transitivedelivery}Transitive delivery]
%%   Transitive delivery ensures the system eventually converges to
%%   optimal partitioning:
%%   \begin{inparaenum}[(i)]
%%   \item (\textbf{termination}) processes do not need to propagate
%%     operations they do not deliver: $\forall \langle i, j \rangle \in
%%     E, \neg d_i(\alpha_{s}^w)\implies \neg
%%     d_j(\alpha_{s}^{w+w_{ij}})$;
%%   \item (\textbf{propagation}) operations delivered by a process may
%%     also benefit neighbor processes: $\forall \langle i, j \rangle \in
%%     E, d_i(\alpha_{s}^{w_1}) \implies
%%     d_j(\alpha_{s}^{w_1+w_{ij}}) \vee
%%     d_j(\alpha_{*}^{w_2 < w_1 + w_{ij}})$.
%%   \end{inparaenum}
%% \end{definition}

\begin{algorithm}
  \input{input/algoadd.tex}
  \caption{\label{algo:add}Adding a partition by Process $p$.}
\end{algorithm}

Algorithm~\ref{algo:add} shows the instructions that implement
eventually consistent partitioning when weights are scalar values.  At
any time, a process running this protocol can add a logical partition
to its distributed system.  Figure~\ref{fig:add} illustrates its
behavior on a system comprising 4 processes $a$, $b$, $c$, and
$d$. Two processes $a$ and $c$ concurrently create a partition by
S-broadcasting their respective \underline{a}dd message: $\alpha_a^0$
and $\alpha_c^0$. They initialize their own state with the lowest
possible bound $0$ (see Line~\ref{line:lowestbound}), and send a
message to each of their neighbors by accumulating the corresponding
edge weight (see Line~\ref{line:accumulator}). In
Figure~\ref{fig:addC}, Process $b$ receives $\alpha_{c}^{1}$. Since it
improves its own partition distance, it keeps it and forwards it to
its neighbors. Process $b$ discards $\alpha_{b}^{1.5}$, for it does
not improve its partition distance. Processes $c$ and $d$ will never
hear of Process $a$'s partition.  In Figure~\ref{fig:addD}, processes
discard last transiting messages. The system converged to the optimal
partitioning.  Transitive relationships ensure that each process gets
its closest source while accumulation of weights ensures that messages
propagation terminates.

%% Interestingly, while the receipt order of messages does not impact on
%% local control information ($r_b(\alpha_a^{1.5}) \cdot
%% r_b(\alpha_a^{1}) \Leftrightarrow r_b(\alpha_a^{1}) \cdot
%% r_b(\alpha_a^{1.5}) \implies \TODO{d_b(\alpha_a^{1})}$), it impacts on
%% control information broadcast in the network ($r_b(\alpha_a^{1.5})
%% \cdot r_b(\alpha_a^{1}) \implies b_b(\alpha_{b}^{1.5}) \cdot
%% b_b(\alpha_{b}^{1})$ while $r_b(\alpha_a^{1}) \cdot
%% r_b(\alpha_a^{1.5}) \implies b_b(\alpha_a^{1})$).

While only adding logical partitions to the distributed system is
straightforward, removing them introduces additional complexity.

\section{Adaptive scoped broadcast}
\label{sec:adaptive}

In this section, we introduce \NAME, a wait-free reactive protocol for
logical partitioning in dynamic distributed systems the cost of which
actually depends on its usage: When the system becomes quiescent,
processes eventually converge to their respective partition and do not
require further communication afterward.

Each process is stateless, works autonomously and asynchronously, in a
peer-to-peer fashion. Each process broadcasts each change to its
neighborhood, for the state of its neighbors may depend on this change
as well. Yet, generated traffic remains \TODO{low} using scoped
broadcast. Messages that carry changes travel through the network
depending on partition of processes, stopping as soon as they
encounter uninterested processes. We demonstrate that \NAME guarantees
consistent partitioning despite different order in message deliveries
from one process to another.

This section starts by describing \NAME's functioning by detailing its
operation to avoid inconsistent states due to ordering and staleness
of delivered messages. This section ends with a complexity analysis of
proposed protocols.

%% \subsection{Intra-autonomous system partitioning}

@@

%% In this section, we aim at solving Problem Statement~\ref{prob:intra}
%% by proposing \NAME, a reactive logical partitioning protocol for
%% dynamic partitioning in dynamic networks.

\paragraph{Dynamic partitions.}
At any time, a process can become a source, hence adding a new
partition to the system. This partition eventually includes all
processes that are closer from this new source than any other else. We
described such protocol in Section~\ref{sec:scoped}. Processes
naturally converge towards their respective best partition by only
piggybacking a monotonically increasing distance in forwarded
messages. % \TODO{Traffic of each partition is contained to the
%  partition.}

@@

%% \subsection{Inter-autonomous system partitioning}

%% \begin{figure}
%%   \centering\input{input/figAS.tex}
%%   \caption{\label{fig:AS}Inter autonomous systems
%%     partitioning. \TODO{More about relative ordering of links at each
%%       process}}
%% \end{figure}

%% In this section, we aim at solving Problem Statement~\ref{prob:inter}
%% by proposing \NAMEB, an extension of \NAME, that enables dynamic
%% logical partitioning in inter-autonomous systems. It leverages
%% hierarchical properties of these networks to further improve on scoped
%% flooding.

%% Autonomous systems are geo-distributed networks. Heterogeneous
%% communication links. Hierarchy of communication links. Per-object
%% broadcast.

%% We leave the link handling to membership protocols~\REF. The ordering
%% of links can be done based on latency. For instance, from 0 to 100 ms,
%% rank 0, from 100 to 1s, rank 2 \ldots

%% \begin{algorithm}
%%   \input{input/algoaaaa.tex}
%%   \caption{\label{algo:aaaa}\NAMEB running at Process $p$ for dynamic
%%     partitioning in inter-autonomous systems.}
%% \end{algorithm}

%% Figure~\ref{fig:AS} shows an example of inter-AS logical partitioning
%% where each process ranks its communication links, and each process
%% forwards messages to its neighbors starting from the rank of the link
%% that triggered the receipt, to its highest rank neighbors. In this
%% example, Process $e$ adds a partition. It forwards the generated
%% message to all its neighbors as if it received it from its lowest rank
%% links. When Process $a$ receives $\alpha_e^1$ from its rank-$0$ link,
%% it forwards it to rank-$0$ links and rank-$1$ links.  Process $b$
%% stops the propagation, for all its links have lower ranks than the one
%% from which it received the message $\alpha_e^2$. Ultimately, the
%% partition includes Process $e$, Process $a$, and Process $b$. Process
%% $c$ and Process $d$ remain unaware of the new \TODO{object}.

%% To ease the reasoning about inter-AS dynamic partitioning in dynamic
%% networks, \NAME runs an independent broadcast protocol for each
%% object, and for each rank of links.  \TODO{Not so easy\ldots}
%% \TODO{Write and describe algo.} \TODO{Overhead of separating things,
%%   slightly more memory, but traffic wise? slower ?}  \TODO{In the
%%   example, not only Process $b$ keeps $e_1$ as its best partition, but
%%   it keeps it for links of rank 0, and links of rank 1.}  When there
%% are no ranking in links, processes solely rely on
%% Algorithm~\ref{algo:adddelundo} for optimal partitioning.

\section{Complexity}
\label{sec:complexity}
